---
title: "Spark44 Deck template"
subtitle: "Example Subtitle"
author: "Donal Phipps"
date: "2017/02/08"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["css/default.css", "css/styles.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class:intro, middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Spark44 template using Xaringan
### A quick test


February 2017

---

# Quick & dirty ninja slides

A quick look at customising slides - adding logo, changing header fonts & colours. Source code at [http://github.com/Phippsy/xaringan](http://github.com/Phippsy/xaringan)

Customised CSS is in the `css/styles.css` file. I have commented out some selectors in the `css/default.css` file to avoid collisions.

Slides will automatically have the company logo added in bottom right (sourced from `img/logo.png`, but you can edit the file in `css/styles.css` - see line 34. Our company decks have a different introduction slide layout so I've jigged things around using an `intro` class (see preceding slide).

---

# With a logo

Quick test to compare the difference between intro logo and main logo slides.

---
class:nologo

# NoLogo slide

Remove the logo using `.nologo` class.

We can also add highlights using the .highlight[highlight] class. Need to look into whether sass is supported for ease of CSS.

---

# Testing a little plot

Users by date, using my wrapper for the marvellous [googleAnalyticsR](http://code.markedmondson.me/googleAnalyticsR/) package.

```{r getdata, message=F, warning=F, fig.width=12, fig.height=4}
library(jlR)
webdata <- get_ga_data()
webdata$plots$Users

```


---

# Testing again

Only thing left to do is add in some text. Below we use `.left-column` and `.right-column` classes for our < ols >, two classes already available in the `default` CSS.

Since all text elements go into divs, we should have good control of size and position through the CSS.

Need to look into the random padding being applied to the top of the .right-column class below, on my todo list...

.left-column[
- Testing
- Testing
- 1,2,3
]

.right-column[
- Testing
- Right
- Column
]

---

# Customisable div width

Using new css classes in our `styles.css` file we can set any column width we like. Should be fairly easy to standardise in a similar fashion to fluid rows from bootstrap.

### 3 columns 

.left-col-3[
One lot of text
]

.left-col-3[
Another lot of text
]

.left-col-3[
Yet more text
]



### 4 columns

.left-col-4[
One lot of text
]

.left-col-4[
Another lot of text
]

.left-col-4[
Yet more text
]

.left-col-4[
Yet more text
]
